This project will use various technologies for both the front-end and the back-end. For the back end, we plan to use an SQL database to store the data, as well as Java servlets for code execution. For the front-end, we plan on using Angular and Javascript for the layout and D3.js for the Visual Transcript instances. We may use jQuery for SQL query manipulation that will serve as input to the algorithm that we formulate that will retrieve the necessary data and spawn a Visual Transcript instance on each view. 

\textnormal{
Transform the project requirements into a system flow diagram, specifyng the different algorithms, data types and structures required for processing and their associated operations.  
The deliverables for this stage include the system flow diagram containing a graphical representation and  textual descriptions of the corresponding data trasnformations, high level pseudo code of the overall system operation, and overall system time and space complexity.}

%\begin{itemize} 
%\item{ }
%A brief textual description of the overall flow diagram (along with its functional operation in the different user scenarios described in the first stage of the project).
%\item{ }
%A specification of each algorithm and associated data structures together with its entities, attributes, and operations ( include an English description of how they relate to your user scenario(s)).

%\end{itemize}
Please insert your deliverables for Stage2 as follows:
\begin{itemize} 
\item{  Short Textual Project Description. }
Please insert here the flow diagram textual description here together with its overall time and space complexity.
\item{ Flow Diagram. }
Please insert your system Flow Diagram here.
\item{ High Level Pseudo Code System Description. }
Please insert high level pseudo-code describing the major system modules as per your flow diagram.
\item{Algorithms and  Data Structures. }
Please insert a brief description of each major Algorithm and its associated data structures here.
\end{itemize}

\begin{itemize} 
\item{  Flow Diagram Major Constraints.}
Please insert here the integrity constraints:
\begin{itemize} 
\item{ Integrity Constraint. }
Please insert the first integrity constraint in here together with its description and justification. 
\end{itemize}
Please repeat the pattern for each integrity constraint.
\end{itemize}
